Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-03-01 additional_files/additional_file_1.tex
Make minor changes to the results (mostly) so that the manuscript reads more easily

@@

\subsubsection*{Maturity group}
\label{annexe-sv-gwas-maturity}

@@

The first GWAS analysis on pubescence form found were signals on chromosomes Gm04 and Gm15 with Platypus
\emph{k}-merss (Figure \ref{pubescence_form_all_manhattan}). However,
upon further analysis of LD patterns, they appeared to be linked to the
\emph{Pa1} locus (Figure \ref{pubescence_form_all_ld}).

>>>>

% Hilum color - T locus
\subsection*{Hilum color -- \textit{T} locus}
\label{annexe-sv-gwas-results-hilum-color-t}

The \textit{T} locus discussed in the main text for pubescence color is also a determining
locus for hilum color. We detected signals overlapping the corresponding gene
using all approaches (Figures \ref{hilum_color_all_manhattan},
\ref{hilum_color_all_T_signal}). The regions defined by the top 5\% (SVs)
and top 1\% (SNPs and \textit{k}-mers) variants included
the Glyma.06g202300 gene associated with this locus. Similarly to what we
observed for the analysis of the \textit{T} locus based on pubescence color, we
did identify the documented causal variant at this locus using the Platypus and
\textit{k}-mer analyses, although these variants were not the most
significantly associated overall (Figures \ref{hilum_color_all_T_gene},
\ref{hilum_color_all_T_kmers}).

% Hilum color - I locus
\subsection*{Hilum color -- \textit{I} locus}
\label{annexe-sv-gwas-results-hilum-color-i}

Similarly, the \textit{I} locus discussed in the main text for its effect on seed coat
color also controls hilum color and we detected signals overlapping the
associated inverted duplication using all approaches (Figures
\ref{hilum_color_all_manhattan}, \ref{hilum_color_all_I_signal}). However,
as was the case for the effect of \textit{I} on seed coat color, we were
not able to link any of the variants identified to the causal variation given
its highly complex nature.

@@

\subsection*{Maturity group}
\label{annexe-sv-gwas-maturity}

@@

The first GWAS analysis on pubescence form found signals on chromosomes Gm04
and Gm15 with SNPs and \emph{k}-mers (Figure
\ref{pubescence_form_all_manhattan}). However, upon further analysis of LD
patterns, they appeared to be linked to the \emph{Pa1} locus (Figure
\ref{pubescence_form_all_ld}).
